
\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlist[itemize]{left=1.2em, itemsep=0.25em, topsep=0.2em, parsep=0em}
\titleformat{\section}{\large\bfseries\uppercase}{\thesection}{0.5em}{}
\titlespacing*{\section}{0pt}{0.4em}{0.2em}

\begin{document}

\begin{center}
{\LARGE \textbf{Francisco (Cisco) Zabala}}\\
California, USA \enspace\textbullet\enspace \href{mailto:zabala@caltech.edu}{zabala@caltech.edu} \enspace\textbullet\enspace \href{https://github.com/datasith}{github.com/datasith} \enspace\textbullet\enspace \href{https://linkedin.com/in/datasith}{linkedin.com/in/datasith} \enspace\textbullet\enspace \href{https://datasith.com}{datasith.com} \enspace\textbullet\enspace (626) 486-6895
\end{center}

\section*{Summary}
Technical leader and domain expert at AWS driving \textbf{GenAI/RAG}, \textbf{agentic AI}, and \textbf{computer vision} solutions for \textbf{U.S. Federal customers} at scale. Deep expertise across the ML stack: model pre-training (MAE, self-supervised learning), multi-agent orchestration, enterprise RAG architectures, and production deployment on AWS. Architected \$10M+ federal engagements spanning Defense, Intelligence, and Civilian agencies; established best practices adopted across 50+ practitioners. Published researcher (Caltech) in CV/robotics with 10+ years shipping production ML systems from notebook to mission-critical deployment. Founder background delivering embedded ML/IoT products at scale.

\section*{Education}
\textbf{California Institute of Technology (Caltech)} \hfill Pasadena, CA\\
Master of Engineering (PhD track), Control \& Dynamical Systems \hfill 2009 -- 2013\\
\textbf{California State University, Fullerton} \hfill Fullerton, CA\\
B.S., Electrical \& Computer Engineering \hfill 2003 -- 2007

\section*{Selected Publications}
\begin{itemize}[leftmargin=*, itemsep=0.15em]
\item E.~I.~Fontaine, F.~Zabala, M.~H.~Dickinson, and J.~W.~Burdick, ``Wing and body motion during flight initiation in \emph{Drosophila} revealed by automated visual tracking,'' \emph{Journal of Experimental Biology}, vol.~212, no.~9, pp.~1307--1323, 2009. \href{https://doi.org/10.1242/jeb.025379}{doi:10.1242/jeb.025379}
\item F.~Zabala, G.~M.~Card, E.~I.~Fontaine, M.~H.~Dickinson, and R.~M.~Murray, ``Flight dynamics and control of evasive maneuvers: the fruit fly's takeoff,'' \emph{IEEE Transactions on Biomedical Engineering}, vol.~56, no.~9, pp.~2295--2298, Sep.~2009. \href{https://doi.org/10.1109/TBME.2009.2027606}{doi:10.1109/TBME.2009.2027606}
\item F.~Zabala, P.~Polidoro, A.~Robie, K.~Branson, P.~Perona, and M.~H.~Dickinson, ``A simple strategy for detecting moving objects during locomotion revealed by animal--robot interactions,'' \emph{Current Biology}, vol.~22, no.~14, pp.~1344--1350, Jul.~2012. \href{https://doi.org/10.1016/j.cub.2012.05.024}{doi:10.1016/j.cub.2012.05.024}
\end{itemize}

\section*{Core Skills}
\textbf{GenAI/LLMs:} RAG architectures, agentic systems (LangGraph, CrewAI, AutoGen), prompt engineering, evaluation frameworks (RAGAS, LangSmith), vLLM, MCP; model fine-tuning, RLHF \enspace \\
\textbf{ML/CV/Foundation Models:} PyTorch, self-supervised pre-training (MAE, DINO), vision transformers, TensorRT, distributed training, model optimization \enspace \\
\textbf{AWS/MLOps:} SageMaker (training, inference, pipelines), Bedrock, S3, EC2, ECR/ECS/EKS, Lambda, Step Functions; Docker, Kubernetes, CI/CD, IaC (CloudFormation, CDK) \enspace \\
\textbf{Data/Systems:} Python, C/C++, SQL, vector databases (Pinecone, FAISS, pgvector), streaming (Kinesis, Kafka), API design \enspace \\
\textbf{Edge/Robotics:} ROS/ROS2, embedded ML (TensorRT, ONNX), camera pipelines, remote sensing, IoT architectures

\section*{Experience}

\textbf{Amazon Web Services (AWS)} \hfill California, USA\\
\textit{Specialty Domain Lead, Agentic AI} \hfill Oct 2024 -- Present
\begin{itemize}
    \item Lead technical strategy and architecture for AWS Professional Services \textbf{U.S. Federal customers}, supporting \$10M+ engagements across Defense, Intelligence, and Civilian agencies in GenAI/agentic AI domains.
    \item Architect enterprise-grade multi-agent systems and RAG solutions for mission-critical applications, ensuring compliance with FedRAMP, ITAR, and IL5/IL6 requirements; drive 30+ technical escalations annually.
    \item Establish best practices and reference architectures for agentic AI spanning IoT edge deployments, computer vision pipelines, and autonomous robotics systems; mentor 15+ data scientists across federal delivery teams.
    \item Design evaluation frameworks for LLM applications including hallucination detection, retrieval quality metrics, and agent reasoning validation for high-assurance environments.
\end{itemize}

\textit{Data Science Lead, Computer Vision} \hfill Sep 2023 -- Oct 2024
\begin{itemize}
    \item Led delivery of 5+ end-to-end CV/IIoT solutions for \textbf{U.S. Federal customers}, architecting scalable pipelines from data ingestion through model deployment and monitoring; reduced time-to-production by 40\% through standardized MLOps frameworks.
    \item Managed cross-functional teams of 5--8 data scientists and ML engineers; established CI/CD best practices, project templates, and code review standards adopted across ProServe federal practice (50+ practitioners).
    \item Designed and deployed real-time inference systems processing 1M+ images daily using SageMaker multi-model endpoints, achieving 99.9\% uptime SLA for mission-critical workloads.
\end{itemize}

\textit{Data Scientist, Computer Vision \& Remote Sensing} \hfill Jul 2022 -- Sep 2023
\begin{itemize}
    \item Pioneered self-supervised pre-training strategies (MAE, SimCLR) for geospatial foundation models, achieving 25\% improvement in downstream object detection tasks with 50\% less labeled data for \textbf{federal defense applications}.
    \item Architected hybrid edge/cloud CV solutions deployed on AWS Panorama and SageMaker Edge Manager, enabling real-time inference at tactical edge with periodic model updates from cloud; reduced bandwidth requirements by 80\%.
    \item Designed distributed training pipelines on SageMaker for vision transformers on satellite imagery datasets (100TB+), optimizing multi-GPU utilization to reduce training time from weeks to days.
\end{itemize}

\vspace{0.2em}
\textbf{Walmart Global Tech / Store No. 8} \hfill California, USA\\
\textit{Sr. Data Scientist, Computer Vision} \hfill Jan 2022 -- Apr 2022
\begin{itemize}
    \item Architected end-to-end ML solutions for three product verticals (inventory, asset protection, customer analytics), establishing scalable training/inference infrastructure on GCP serving 4,700+ stores.
    \item Led technical design for nationwide rollout of edge CV systems, optimizing model architectures (MobileNet, EfficientDet) for Android devices to achieve <100ms inference latency while maintaining 95\%+ accuracy.
\end{itemize}

\textit{Research Scientist, Store No. 8 (Incubator)} \hfill Aug 2021 -- Jan 2022
\begin{itemize}
    \item Co-led ML development for fastest incubation-to-production project in Store No. 8 history (5 months); designed hybrid heuristic/deep-learning pipeline for real-time shelf monitoring achieving 92\% accuracy.
    \item Built data collection and annotation infrastructure supporting 50K+ labeled images weekly; established model evaluation frameworks adopted company-wide.
\end{itemize}

\vspace{0.2em}
\textbf{ACROBOTIC} \hfill Pasadena, CA\\
\textit{Founder} \hfill Jan 2013 -- Aug 2021
\begin{itemize}
    \item Led engineering teams to deliver custom-built instruments for ML, IoT, robotics, and remote sensing applications.
    \item Drove customer adoption across DIY communities and National Lab engineers with purpose-built HW/SW products.
\end{itemize}

\vspace{0.2em}
\textbf{California Institute of Technology (Caltech)} \hfill Pasadena, CA\\
\textit{Graduate Research Assistant} \hfill Sep 2008 -- Dec 2012
\begin{itemize}
    \item Built high-speed videography pipelines and real-time analysis for animal flight experiments.
    \item Applied unsupervised learning to track 3D wing/body kinematics in fruit-fly flight.
\end{itemize}

\textit{Visiting Scientist, DARPA Urban Challenge} \hfill Mar 2007 -- Aug 2008
\begin{itemize}
    \item Implemented vision algorithms for first-gen driverless navigation; contributed to vehicle retrofitting for autonomy.
\end{itemize}

\section*{Selected Projects}
\textbf{Multi-Agent RAG System for Federal Intelligence Analysis} \emph{(Python, LangGraph, AWS Bedrock, SageMaker)}\\
Architected production multi-agent orchestration system with specialized reasoning agents for document analysis, leveraging Claude 3.5 Sonnet and retrieval from pgvector; implemented evaluation framework achieving 95\% answer accuracy on classified datasets.
\\[0.25em]
\textbf{Geospatial Foundation Model with MAE Pre-training} \emph{(Python, PyTorch, SageMaker, Vision Transformers)}\\
Designed self-supervised pre-training pipeline using Masked Autoencoders (MAE) on 100TB+ satellite imagery corpus; achieved SOTA results on downstream object detection tasks with 50\% less labeled data; deployed distributed training across 32 GPUs.
\\[0.25em]
\textbf{Agentic Robotics System for Autonomous Inspection} \emph{(Python, ROS2, AWS IoT, LangChain)}\\
Built autonomous inspection robot combining CV perception, LLM-based task planning, and multi-modal reasoning; deployed on AWS edge infrastructure with real-time telemetry and remote model updates.
\\[0.25em]
\textbf{Real-Time Edge CV for Retail Inventory} \emph{(Python, TensorRT, TensorFlow Lite, Android)}\\
Deployed optimized object detection models (EfficientDet) on 4,700+ Android devices achieving <100ms latency; designed hybrid cloud/edge architecture for continuous model improvement from production data.

\section*{Certifications \& Security Clearances}
AWS Certified Machine Learning -- Specialty \enspace\textbullet\enspace AWS Certified AI Practitioner \enspace\textbullet\enspace AWS Certified Security -- Specialty \enspace\textbullet\enspace AWS Certified Data Analytics -- Specialty \enspace\textbullet\enspace AWS Certified Database -- Specialty \enspace\textbullet\enspace AWS Certified Machine Learning Engineer -- Associate \enspace\textbullet\enspace AWS Certified Data Engineer -- Associate \enspace\textbullet\enspace AWS Certified Solutions Architect -- Associate \enspace\textbullet\enspace AWS Certified Developer -- Associate \enspace\textbullet\enspace CompTIA Security+

% Add your security clearance information here if applicable, e.g.:
% \vspace{0.3em}
% \textbf{Active Security Clearance:} Secret / Top Secret (specify level and date)

\end{document}
